---
title: "Business Intelligence Project"
author: "<Specify your name here>"
date: "<Specify the date when you submitted the lab>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

|                                              |                             |
|--------------------------------------------|----------------------------|
| *Student ID Number*                        | 135129,122147,120578,121774,121619 |
| *Student Name*                             | Avengers                     |
| *BBIT 4.2 Group*                           | B                       |
| *BI Project Group Name/ID (if applicable)* | Avengers                      |

# Setup Chunk

*Note:* the following KnitR options have been set as the global defaults: <BR> knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy = TRUE).

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = FALSE
)
```{r}
retail <- read_excel("data/Online Retail.xlsx")
dim(retail)
```
```{r}
train_index <- createDataPartition(retail$UnitPrice,
                                   p = 0.8,
                                   list = FALSE)
retail_train <- retail[train_index, ]
retail_test <- retail[-train_index, ]
```

