---
title: "Business Intelligence Project"
author: "<Specify your name here>"
date: "<Specify the date when you submitted the lab>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
  markdown: 
    wrap: 72
---

# Student Details

|                                            |                                    |
|--------------------------------------------|----------------------------|
| *Student ID Number*                        | 135129,122147,120578,121774,121619 |
| *Student Name*                             | Avengers                           |
| *BBIT 4.2 Group*                           | B                                  |
| *BI Project Group Name/ID (if applicable)* | Avengers                           |

# Setup Chunk

*Note:* the following KnitR options have been set as the global
defaults: <BR> knitr::opts_chunk\$set(echo = TRUE, warning = FALSE, eval
= TRUE, collapse = FALSE, tidy = TRUE).

More KnitR options are documented here
<https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and
here <https://yihui.org/knitr/options/>.

{r setup, include=FALSE} library(formatR) knitr::opts_chunk\$set(
warning = FALSE, collapse = FALSE )

# Load and split the dataset

```{r}
library(AER)
data("Affairs")
```

# Test data split of the dataset

```{r}
library(caret)
train_index <- createDataPartition(Affairs$age,
                                   p = 0.8,
                                   list = FALSE)
affairs_train <- Affairs[train_index, ]
affairs_test <- Affairs[-train_index, ]
```

## Train the model

```{r}
set.seed(7)
train_control <- trainControl(method = "cv", number = 5)
affairs_caret_model_lm <- train(age ~ ., data = affairs_train,
                                       method = "lm", metric = "RMSE",
                                       preProcess = c("center", "scale"),
                                       trControl = train_control)



```

## Display the model's details

```{r}
print(affairs_caret_model_lm)

```

## Make predictions

```{r}
predictions <- predict(affairs_caret_model_lm,
                       affairs_test[, 1:9])
```

## Display the model's evaluation metrics

```{r}
rmse <- sqrt(mean((affairs_test$age - predictions)^2))
print(paste("RMSE =", sprintf(rmse, fmt = "%#.4f")))

```

## SSR

```{r}
ssr <- sum((affairs_test$age - predictions)^2)
print(paste("SSR =", sprintf(ssr, fmt = "%#.4f")))

```

## SST

```{r}
sst <- sum((affairs_test$age - mean(affairs_test$age))^2)
print(paste("SST =", sprintf(sst, fmt = "%#.4f")))
```

## R Squared

```{r}
r_squared <- 1 - (ssr / sst)
print(paste("R Squared =", sprintf(r_squared, fmt = "%#.4f")))
```

## MAE

```{r}
absolute_errors <- abs(predictions - affairs_test$age)
mae <- mean(absolute_errors)
print(paste("MAE =", sprintf(mae, fmt = "%#.4f")))
```

## Logistic Regression

## Train the model

```{r}
affairs_model_glm <- glm(children ~ ., data = affairs_train,
                          family = binomial(link = "logit"))

```

## Display the model's details

```{r}
print(affairs_model_glm)
```

## Make predictions

```{r}
probabilities <- predict(affairs_model_glm, affairs_test[, 1:9],
                         type = "response")
print(probabilities)
predictions <- ifelse(probabilities > 0.5, "pos", "neg")
print(predictions)
```

## Display the model's evaluation metrics

```{r}
table(predictions, affairs_test$children)
```

## Logistic Regression with caret

```{r}
train_control_reg <- trainControl(method = "cv", number = 5)
set.seed(7)
affairs_caret_model_logistic <-
  train(children ~ ., data = affairs_train,
        method = "regLogistic", metric = "Accuracy",
        preProcess = c("center", "scale"), trControl = train_control)
print(affairs_caret_model_logistic)
```

## Make predictions

```{r}
predictions <- predict(affairs_caret_model_logistic,
                       affairs_test[, 1:9])
```

## Display the model's evaluation metrics

```{r}
confusion_matrix <-
  caret::confusionMatrix(predictions,
                         affairs_test[, 1:9]$children)
print(confusion_matrix)

fourfoldplot(as.table(confusion_matrix), color = c("grey", "lightblue"),
             main = "Confusion Matrix")

```

## Linear Discriminant Analysis with caret

## Train the model

```{r}
set.seed(7)
train_control <- trainControl(method = "LOOCV")
affairs_caret_model_lda <- train(children ~ .,
                                  data = affairs_train,
                                  method = "lda", metric = "Accuracy",
                                  preProcess = c("center", "scale"),
                                  trControl = train_control)
print(affairs_caret_model_lda)
```

## Make predictions

```{r}
predictions <- predict(affairs_caret_model_lda,
                       affairs_test[, 1:9])
```

## Display the model's evaluation metrics

```{r}
confusion_matrix <-
  caret::confusionMatrix(predictions,
                         affairs_test[, 1:9]$children)
print(confusion_matrix)

fourfoldplot(as.table(confusion_matrix), color = c("grey", "lightblue"),
             main = "Confusion Matrix")
```

## Regularized Linear Regression Classification Problem without CARET

```{r}
x <- as.matrix(Affairs[, 1:9])
y <- as.matrix(Affairs[, 9])
```

## Display the model's details

```{r}
print(affairs_model_glm)

```

## Make predictions

```{r}
predictions <- predict(affairs_model_glm, x, type = "link")
```

## Regularized Linear Regression Classification Problem with CARET Load and split the dataset

```{r}
data(affairs)
```

## Define a 70:30 train:test data split of the dataset

```{r}
train_index <- createDataPartition(Affairs$children,
                                   p = 0.7,
                                   list = FALSE)
affairs_train <- Affairs[train_index, ]
affairs_test <- Affairs[-train_index, ]
```
