---
title: "Business Intelligence Project"
author: "<Specify your name here>"
date: "<Specify the date when you submitted the lab>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
  markdown: 
    wrap: 72
---

# Student Details

|                                            |                                    |
|--------------------------------------------|----------------------------|
| *Student ID Number*                        | 135129,122147,120578,121774,121619 |
| *Student Name*                             | Avengers                           |
| *BBIT 4.2 Group*                           | B                                  |
| *BI Project Group Name/ID (if applicable)* | Avengers                           |

# Setup Chunk

*Note:* the following KnitR options have been set as the global
defaults: <BR> knitr::opts_chunk\$set(echo = TRUE, warning = FALSE, eval
= TRUE, collapse = FALSE, tidy = TRUE).

More KnitR options are documented here
<https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and
here <https://yihui.org/knitr/options/>.

{r setup, include=FALSE} library(formatR) knitr::opts_chunk\$set(
warning = FALSE, collapse = FALSE )

# Load and split the dataset

```{r}
retail <- read_excel("data/Online Retail.xlsx")
dim(retail)
```

# Test data split of the dataset

```{r}
train_index <- createDataPartition(retail$UnitPrice,
                                   p = 0.8,
                                   list = FALSE)
retail_train <- retail[train_index, ]
retail_test <- retail[-train_index, ]
```

```         
```

# Handle missing values

## Are there missing values in the dataset?

```{r}
any_na(retail)
```

## How many?

```{r}
n_miss(retail)
```

## What is the proportion of missing data in the entire dataset?

```{r}
prop_miss(retail)
```

## What is the number and percentage of missing values grouped by each variable?

```{r}
miss_var_summary(retail)
```

## Which variables contain the most missing values?

```{r}
gg_miss_var(retail)
```

## Which combinations of variables are missing together?

```{r}
gg_miss_upset(retail)
```

## Remove the observations with missing values 

```{r}
retail_removed_obs <- retail %>% filter(complete.cases(.))
```

## We end up with 406,829 observations to create the association rules instead of the initial 541,909 observations.

```{r}
dim(retail_removed_obs)
```

## Are there missing values in the dataset?

```{r}
any_na(retail_removed_obs)
```
